
\subsection{Conferences and Workshops}

\datedsubsectionnarrow{Apr 2024}
{Autrans, France}
{\emph{Submanifolds of locally symmetric spaces: geometric, analytic and dynamical}}
{\emph{{\normalsize aspects},} \begin{footnotesize}
		workshop.
\end{footnotesize}}

%\conference{Feb 2024}{Universit\'a degli Studi di Pavia}{TBA}{workshop}

\conference{Jul 2023}{ICMAT, El Barco de {\'A}vila, Spain}{Group actions and low-dimensional topology}{conference}

\conference{Jan \nth{27}, 2023}{MPI for MiS, Leipzig, Germany}{Geometry, topology, and their applications}{online workshop}

\conference{Aug \nth{22}-\nth{26}, 2022}{Autrans, France}{Minimal surfaces in symmetric spaces and Labourie's conjecture}{workshop}

\conference{Jul \nth{20}, 2022}{Universit\'e Grenoble Alpes}{AMS-EMS-SMF Meeting}{conference}

\conference{Mar \nth{12}, 2022}{Baylor University}{\nth{55} Spring Topology and Dynamics Conference}{conference}

\conference{Jun 2021}{Online}{Nearly Carbon Neutral Geometric Topology Conference}{online conference}

\conference{Aug 2019}{Chiang Mai University}{Combinatorial and algebraic aspects of geometric structures}{conference}

\conference{Dec \nth{8}, 2020}{GDR Platon}{Parole aux jeunes g\'eom\`etres dynamiques}{online workshop}

\conference{Sep 2018}{INRIA Nancy - Grand Est}{Young Mathematicians Symposium of the Greater Region}{conference}

\conference{May 2018}{INRIA Nancy - Grand Est}{Structures on Surfaces}{workshop}

\subsection{Seminars}

\datedsubsectionnarrow{Mar \nth{18}, 2024}
{Universit\'e du Luxembourg}
{Geometry Seminar.}
{}

\datedsubsectionnarrow{Feb \nth{15}, 2024}
{Institut Fourier, Grenoble}
{S\'eminaire de Th\'eorie Spectrale et G\'eom\'etrie.}
{}

\datedsubsectionnarrow{Oct \nth{10}, 2023}
{MPI for MiS}
{Geometry Seminar.}
{}

\datedsubsectionnarrow{Mar \nth{6}, 2023}
{University of Wisconsin-Madison}
{Dynamics Seminar.}
{}

\datedsubsectionnarrow{Jan \nth{13}, 2023}
{UC Riverside}
{Colloquium talk.}
{}

\datedsubsectionnarrow{Nov \nth{28}, 2022}
{UT Austin}
{Topology Seminar.}
{}

\datedsubsectionnarrow{Nov \nth{18}, 2022}
{UC Riverside}
{Geometry-Topology Seminar.}
{}

\datedsubsectionnarrow{Apr \nth{4}, 2022}
{University of Virginia}
{Geometry Seminar.}
{}

\datedsubsectionnarrow{Nov \nth{29}, 2021}
{University of Maryland}
{Geometry-Topology Seminar.}
{}

\datedsubsectionnarrow{Jun \nth{10}, 2021}
{Heidelberg University}
{Differential Geometry Seminar (online).}
{}

\datedsubsectionnarrow{May \nth{11}, 2021}
{University of Virginia}
{Geometry Seminar.}
{}

\datedsubsectionnarrow{Nov \nth{3}, 2020}
{Online}
{Pangolin Seminar.}
{}

\datedsubsectionnarrow{Oct \nth{14}, 2020}
{University of Utah}
{Max Dehn Seminar.}
{}

\datedsubsectionnarrow{Feb \nth{12}, 2020}
{Texas A\&M}
{Topology Seminar.}
{}

\datedsubsectionnarrow{Jan \nth{30}, 2020}
{Boston College}
{Geometry \& Topology Seminar.}
{}

\datedsubsectionnarrow{Jan \nth{28}, 2020}
{Yale University}
{Geometry \& Topology Seminar.}
{}

\datedsubsectionnarrow{Jan \nth{23}, 2020}
{Heidelberg University}
{Differential Geometry Seminar.}
{}

\datedsubsectionnarrow{Dec \nth{12}, 2019}
{Institut Fourier, Grenoble}
{S\'eminaire de Th\'eorie Spectrale et G\'eom\'etrie.}
{}

\datedsubsectionnarrow{Feb \nth{19}, 2019}
{University of Virginia}
{Geometry Seminar.}
{}


